### 2020-04-26 final_report/methodology.tex
add some more SMT references

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
		Gaussian process regression	& GPR & SciKit Learn & 2 \\
		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
		Inverse distance weighing & IDW & SMT~\cite{SMT2019} & 1 \\
		Radial basis functions & RBF & SMT & 3 \\
		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
		Ridge regression & RR & SciKit Learn & 4 \\
		Kriging & KRG & SMT & 4 \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}

>>>>

\begin{table}[h]
	\centering
	{\footnotesize
		\begin{tabular}{llll}
		\toprule
		Surrogate & Acronym & Implementation & Hyperparameters \\
		\midrule
		Support vector machines	& SVM & SciKit Learn~\cite{scikit-learn} & 3 \\
		Gradient boosted trees	& GBT & SciKit Learn & 11 \\
		Extremely randomized trees	& ERT & SciKit Learn & 7 \\
		AdaBoosted decision trees	& AB & SciKit Learn & 3 \\
		Gaussian process regression	& GPR & SciKit Learn & 2 \\
		$k$ nearest neighbours	& KNN & SciKit Learn & 3 \\
		Artificial neural networks	& ANN & Keras (TensorFlow)~\cite{chollet2015keras} & 2 \\
		Inverse distance weighing~\cite{shepard1968two} & IDW & SMT~\cite{SMT2019} & 1 \\
		Radial basis functions & RBF & SMT & 3 \\
		Stochastic gradient descent & SGD & SciKit Learn & 13 \\
		Ridge regression & RR & SciKit Learn & 4 \\
		Kriging~\cite{sacks1989designs,wold1975soft,bouhlel2016improving,bouhlel2016improved} & KRG & SMT & 4 \\
		\bottomrule
		\end{tabular}
	}
	\caption{Considered surrogate model classes.}
	\label{tbl:surrogates}
\end{table}
